---
title: "Test Read PDF"
author: "Paul Leiby"
date: "6/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Extract text from pdf in R and word Detection
---------------------------------------------

```{r}
# install.packages("pdftools")
```

```{r loadLibrary}
library(pdftools)
library(stringr)
library(tidyverse)
```


#### [Eastport Municipal Tax Rate](https://www.eastport-me.gov/department-assessing/pages/municipal-tax-rate)

Taxes:

Real Estate and Personal Property. The assessment date for the State of Maine is April 1st of each year. Any changes in ownership after that date will be made after commitment in July or August.  Effort will be made to mail a copy of the tax bill to the new property owner as well.  Generally, the City Council approves the annual budget in June/July and tax bills are issued by early August.  Please read the "Taxpayer Notice" on the bill to avoid any possible confusion.

FISCAL YEAR: July 1st-June 30th

ASSESSMENT: 97%

FY 2015 TAX RATE: $26.00

TAXES DUE: October 31, 2019

INTEREST: 7.00% as of November 2, 2020 (rate set annually)

#### [Eastport Tax Maps](https://www.eastport-me.gov/sites/g/files/vyhlif536/f/uploads/city_of_eastport_tax_maps_october_2016.pdf)

#### Location of Assessment "Commitment Book" Files

```{r}
filename <- "Eastport_Assessor fy_2020_commitment_book.pdf"

commitmentbook_2019_url <- "https://www.eastport-me.gov/department-assessing/files/fy-2019-tax-commitment-book"
commitmentbook_2020_url <- "https://www.eastport-me.gov/sites/g/files/vyhlif536/f/pages/fy_2020_commitment_book.pdf"
commitmentbook_2021_url <- "https://www.eastport-me.gov/sites/g/files/vyhlif536/f/uploads/fy21_real_estate_commitment_book_8-05-2020.pdf"
```

```{r}
file_downloaded = TRUE

if (!file_downloaded) {
    download.file(commitmentbook_2020_url, destfile = filename, mode = "wb")
    file_downloaded = TRUE
}
```

`pdf_text()` function, which returns a character vector of length equal to the number of pages in the file.

#### Extract Text from pdf in R

Extract the text from all pages.


```{r}
pdf_text <- pdftools::pdf_text(filename)
```


The result is a character vector (vector of character strings),
each page being one string.

```{r}
class(pdf_text)
```

```{r}
str(pdf_text)
```

Display of first page

```{r}
cat(pdf_text[1])
```


To extract a particular word from these pages, unlist the data and convert it into lower case letters

```{r}
taxdata <- unlist(pdf_text) # does this do anything?
# taxdata <- tolower(taxdata)
class(taxdata)
```

Extract the page number for pages containing a particular name.

```{r}
res <- data.frame(str_detect(taxdata, "leiby"))
colnames(res) <- "NameFound"

res <- subset(res, res$NameFound == TRUE)

row.names(res)
```

Processing
----------

- Add page numbers (confirm they can be read from end of line 1 on each page)
- Strip header 3 lines from each page (confirming content, reading page number and headings)

        Eastport                       Real Estate Tax Commitment Book - 26.200                            08/06/2019
        12:20 PM                                     FY20 REAL ESTATE COMMITMENT                          Page      1
        "^Account Name & Address                        Land     Building    Exemption       Assessment            Tax"

- Strip 3 lines from end of each page:
    - headings "^[ ]+Land           Building             Exempt         Total               Tax"
    - "^Page Totals;"
    - "^Subtotals:" | "^Final Totals:"
- Strip Final Totals from last page
- Process page by page
- Break each page into Assessment records
    - last 3-4 lines are Address, Lot number and record pages - date
- Strip of Page Totals

Analysis
-----------
- Compare valuation of land across records
- COmpare valuation of land w/o Buildings
- Compare valuation of land in proximity

- Compare valuations to Redfin or Zillow?


#### Last Page

```{r}
length(taxdata)
cat(taxdata[length(taxdata)])
```

- Note "Acres" and it value is usually on 2nd line of record, under "Land" column, but not if name is > certain length.
- may be able to use fixed-width for each field, but spacing may not be exactly preserved.
- note pdf read does an amazingly good job of retaining leading white space and internal white space on line
    - it also includes blank lines as "\n"
    - but it drops trailing white space on each line.

Example of a line starting with 
```{r}
str_detect(taxdata, "\n    1")
```

#### Raw content of a page:

```{r}
taxdata[1]
```

