---
title: "Test Read PDF"
author: "Paul Leiby"
date: "6/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Extract text from pdf in R and word Detection
---------------------------------------------

by [finnstats, Posted on June 15, 2021](https://finnstats.com/index.php/2021/06/15/extract-text-from-pdf-in-r-and-word-detection/)

Extract text from pdf in R, first we need to install pdftools package from cran.

Let’s install the pdftools package from cran.

```{r}
# install.packages("pdftools")
```

Load the package

```{r}
library("pdftools")
```

The pdf file needs to save in local directory or get it from online. Here we are extracting one sample document from online.

Store the link in pdf_file variable.

```{r}
pdf_file <- "https://file-examples-com.github.io/uploads/2017/10/file-sample_150kB.pdf"
```


Let’s download the demo pdf file into the local directory

```{r}
download.file(pdf_file, destfile = "sample.pdf", mode = "wb")
```

`pdf_text()` function, which returns a character vector of length equal to the number of pages in the file.

#### Extract text from pdf in R

Extract the text from all pages.

```{r}
pdf_text <- pdftools::pdf_text("sample.pdf")
```

Suppose if you want to display second page information then use below code,

```{r}
cat(pdf_text[[2]])
```

Displayed only a few text here

    In non mauris justo. Duis vehicula mi vel mi pretium, a viverra erat efficitur. Cras aliquam
    est ac eros varius, id iaculis dui auctor. Duis pretium neque ligula, et pulvinar mi placerat
    et. Nulla nec nunc sit amet nunc posuere vestibulum. Ut id neque eget tortor mattis
    tristique. Donec ante est, blandit sit amet tristique vel, lacinia pulvinar arcu. Pellentesque
    scelerisque fermentum erat, id posuere justo pulvinar ut. Cras id eros sed enim aliquam
    lobortis. Sed lobortis nisl ut eros efficitur tincidunt. Cras justo mi, porttitor quis mattis vel, ultricies ut purus. Ut facilisis et lacus eu cursus.

To extract a particular word from these pages, unlist the data and convert it into lower case letters

```{r}
str(pdf_text)
```

```{r}
pdf_text <- unlist(pdf_text)
pdf_text <- tolower(pdf_text)
```

Suppose if we want to extract the page number details for the word contains “Suspendisse“

```{r}
library(stringr)

res <- data.frame(str_detect(pdf_text, "suspendisse"))
colnames(res) <- "Result"
res <- subset(res, res$Result == TRUE)
row.names(res)
```

Output

    1] "2" "3"

The word “suspendisse” contains on pages number 2 and 3.


```{r}
filename <- "Eastport_Assessor fy_2020_commitment_book.pdf"
```


```{r}
pdf_text <- pdftools::pdf_text(filename)
str(pdf_text)
```

```{r}
cat(pdf_text[1])
```

Processing
----------

- Add page numbers (confirm they can be read from end of line 1 on each page)
- Strip header 3 lines from each page (confirming content, reading page number and headings)

        Eastport                       Real Estate Tax Commitment Book - 26.200                            08/06/2019
        12:20 PM                                     FY20 REAL ESTATE COMMITMENT                          Page      1
        "^Account Name & Address                        Land     Building    Exemption       Assessment            Tax"
- Strip 3 lines from end of each page:
    - (headings "^[ ]+Land           Building             Exempt         Total               Tax"
    - "^Page Totals;"
    - "^Subtotals:" | "^Final Totals:"
- Strip Final Totals from last page

- Process page by page
- Break each page into Assessment records
    - last 3-4 lines are Address, Lot number and record pages - date
- Strip of Page Totals

Analysis
-----------
- Compare valuation of land across records
- COmpare valuation of land w/o Buildings
- Compare valuation of land in proximity

- Compare valuations to Redfin or Zillow?


#### Last Page

```{r}
length(pdf_text)
cat(pdf_text[length(pdf_text)])
```

- Note "Acres" and it value is usually on 2nd line of record, under "Land" column, but not if name is > certain length.
- may be able to use fixed-width for each field, but spacing may not be exactly preserved.
- note pdf read does an amazingly good job of retaining leading white space and internal white space on line
    - it also includes blank lines as "\n"
    - but it drops trailing white space on each line.

Example of a line starting with 
```{r}
str_detect(pdf_text, "\n    1")
```

#### Raw content of a page:

```{r}
pdf_text[1]
```

