---
title: "Test Read PDF"
author: "Paul Leiby"
date: "6/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Extract text from pdf in R and word Detection
---------------------------------------------

by [finnstats, Posted on June 15, 2021](https://finnstats.com/index.php/2021/06/15/extract-text-from-pdf-in-r-and-word-detection/)

Extract text from pdf in R, first we need to install pdftools package from cran.

Let’s install the pdftools package from cran.

```{r}
# install.packages("pdftools")
```

Load the package

```{r}
library("pdftools")
```

The pdf file needs to save in local directory or get it from online. Here we are extracting one sample document from online.

Store the link in pdf_file variable.

```{r}
pdf_file <- "https://file-examples-com.github.io/uploads/2017/10/file-sample_150kB.pdf"
```


Let’s download the demo pdf file into the local directory

```{r}
download.file(pdf_file, destfile = "sample.pdf", mode = "wb")
```

`pdf_text()` function, which returns a character vector of length equal to the number of pages in the file.

#### Extract text from pdf in R

Extract the text from all pages.

```{r}
pdf_text <- pdftools::pdf_text("sample.pdf")
```

Suppose if you want to display second page information then use below code,

```{r}
cat(pdf_text[[2]])
```

Displayed only a few text here

    In non mauris justo. Duis vehicula mi vel mi pretium, a viverra erat efficitur. Cras aliquam
    est ac eros varius, id iaculis dui auctor. Duis pretium neque ligula, et pulvinar mi placerat
    et. Nulla nec nunc sit amet nunc posuere vestibulum. Ut id neque eget tortor mattis
    tristique. Donec ante est, blandit sit amet tristique vel, lacinia pulvinar arcu. Pellentesque
    scelerisque fermentum erat, id posuere justo pulvinar ut. Cras id eros sed enim aliquam
    lobortis. Sed lobortis nisl ut eros efficitur tincidunt. Cras justo mi, porttitor quis mattis vel, ultricies ut purus. Ut facilisis et lacus eu cursus.

To extract a particular word from these pages, unlist the data and convert it into lower case letters

```{r}
str(pdf_text)
```

```{r}
pdf_text <- unlist(pdf_text)
pdf_text <- tolower(pdf_text)
```

Suppose if we want to extract the page number details for the word contains “Suspendisse“

```{r}
library(stringr)

res <- data.frame(str_detect(pdf_text, "suspendisse"))
colnames(res) <- "Result"
res <- subset(res, res$Result == TRUE)
row.names(res)
```

Output

    1] "2" "3"

The word “suspendisse” contains on pages number 2 and 3.

